UniScatter: Unifying\\Backscatter Communications, Reconfigurable Intelligent Surface, and Symbiotic Radio

### 2022-08-02 main.tex
:pencil: Update introduction

\begin{section}{Introduction}
	% TODO You need to explain the key principle and benefits of backscatter, then symbiotic radio, then RIS. Then you need to explain about the apparent differences and similarities between those techniques. Then metascatter concept will appear.
	% The evolution of wireless communications
	% \IEEEPARstart{I}{nternet-of-Everything} is envisioned to provide high throughput, ultralow power, ubiquitous distribution, and connected intelligence for future wireless networks.
	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, ultralow power, ubiquitous deployment, and connected intelligence for trillions of portable devices.
	% \gls{bc} is an emerging technique that allows low-power devices to transmit without power-hungry \gls{rf} components.
	% An emerging technique for low-power communication is \gls{bc}, which allows backscatter node to embed its own message over
	% An emerging technique for low-power communication is \gls{bc}, which allows information node to embed its own message over
	% transmit without active \gls{rf} components
	% \gls{bc} is an emerging technique that allows information nodes to alter scattered electromagnetic field and transmit without onboard \gls{rf} components (e.g., carrier syntheizer and power amplifier).
	% \gls{bc} is an emerging technique that allows information nodes to operate over surrounding carrier wave and transmit without onboard \gls{rf} components.
	\gls{bc} is an emerging technique that allows backscatter nodes to operate over dedicated carrier signal without onboard \gls{rf} components (e.g., carrier syntheizer and power amplifier).
	The low-power nodes harvest energy from incident wave and modulate information over scattered signal.

>>>>

\begin{section}{Introduction}
	% TODO You need to explain the key principle and benefits of backscatter, then symbiotic radio, then RIS. Then you need to explain about the apparent differences and similarities between those techniques. Then metascatter concept will appear.
	% The evolution of wireless communications
	% \IEEEPARstart{I}{nternet-of-Everything} is envisioned to provide high throughput, ultralow power, ubiquitous distribution, and connected intelligence for future wireless networks.
	% \IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, massive connectivity and heterogeneous control for trillions of portable devices with ultralow power consumption.
	\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
	% \gls{bc} is an emerging technique
	% that enables low-power communication by separating the
	% As an emerging low-power communication technique, \gls{bc} separates the power-hungry \gls{rf} components (i.e., synthesizer and amplifier) as dedicated carrier emitter, and employs passive energy harvester and impedance modulator to operate over incident and scattered signals.
	% As an emerging low-power communication technique, \gls{bc} separates the power-hungry \gls{rf} components (i.e., synthesizer and amplifier) as dedicated carrier emitter, and equips the backscatter node with energy harvester and load-switching modulator to operate over incident and scattered signals, respectively.
	As an emerging low-power communication technique, \gls{bc} separates the power-hungry \gls{rf} elements (e.g., synthesizer and amplifier) as dedicated carrier emitter, and leaves the passive components (e.g., harvester and modulator) at the backscatter node.
	The node harvests energy from emitted \gls{rf} wave and embeds its information over scattered signal.
